Meta-analytic approaches and 'new' effect sizes to account for heterogeneous effects in comparative physiology

### 2021-05-25 MS/ms.Rmd
Udpated the inclusion paragraph

We excluded plant meta-analyses because they were often focused on ecological (e.g., quantified changes in abundance and distribution of species) or agricultural questions (e.g., studies on soil microbial function, nitrogen and phosphorus capture, methane output and greenhouse gas emissions) that did not focus on organism physiological function across species. Meta-analyses needed to have collected physiological trait data from the literature including traits, such as hormones, thermal physiology (CTmax, CTmin, thermal preferences, thermal breadth, LT50, lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress and consequences (e.g., DNA damage, teleomere attrition), performance measurements (heart rates, sprint speed, swim speed, growth rates) and immune traits (cell function, antibodies, ect). Studies were also included if they measured reproductive allocation, survival / mortality or quantified scaling relationships with body size (e.g., metabolic scaling) across taxa. Studies on behavior were only included if they were explicitly interested in proximate physiological drivers of behavioral variation. Meta-analyses quantifying phenology, differences in body sizes between the sexes (i.e., SSD) and those focused on validating physiological methodology were excluded because the underlying question was not physiological in nature. While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature.

>>>>

We included quantitative syntheses, including meta-analyses (*sensu stricto*), that were focused on comparative physiologcial questions. Narrative reviews and comments were not considered because they did not collate quantitative data from the literature. Studies needed to have collected physiological trait data from the literature including traits, such as hormones, thermal physiology (CTmax, CTmin, thermal preferences, thermal breadth, LT50, lethal thresholds), metabolic rates (routine, maximum, and minimum metabolic rate, aerobic scope), enzyme reaction rates and concentrations, oxidative stress and consequences (e.g., DNA damage, teleomere attrition), performance measurements (e.g., heart rates, sprint speed, swim speed, growth rates), body composition (e.g., fatty acid profiles) and immune traits (e.g., cell function, antibodies, ect.). Studies were also included if they measured the relationship between physiological traits and body size (e.g., metabolic scaling), reproductive allocation, or survival / mortality across taxa. Studies on behavior were only included if the synthesis was explicitly interested in the proximate physiological drivers of behavioral variation. We also included meta-analyses that quantify plasticity in physiological traits across taxa for the purpose of understanding adaptive plasticity in response to environmental variation. While many studies in comparative physiology collect data as part of a comparative analysis, we focus here only on studies collating data from existing literature because this is the major data source for quantitative synthesis. Quantitative syntheses interested in phenology, biomechanics, sexual size dimorphism (i.e., SSD, except if the study was interested in sexual differences in physiological traits), those focused on validating physiological methodology, or characterising population genetic structure, gene transcription and quantitative genetics were excluded. There were also meta-analyses that focused on colour evolution and contrast which varied in their goals but were most often not focused on physiological questions. As such, these studies were also exclude.  We also excluded plant synthesis papers because they were often focused on ecological (e.g., quantified changes in abundance and distribution of species) or agricultural questions (e.g., studies on soil microbial function, nitrogen and phosphorus capture, methane output and greenhouse gas emissions) that did not focus on organism physiological function across species.
